---
title: "Social Vulnerability Index (2019)"
author: "René Dario Herrera for Coconino County"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE, comment=FALSE, dpi=150, echo=FALSE, message=FALSE, warning=FALSE)

# setup
# packages 
library(here)
library(sf)
library(tidyverse)

# data 
census_tract_data_spatial <- read_rds("../data/census_tract_data_spatial.rds")
```

# total population 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = totpop)) +
  scale_fill_viridis_b() +
  theme_void()
```

# adaptive_capacity_index

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = adaptive_capacity_index)) +
  scale_fill_viridis_b() +
  theme_void()
```

# living in poverty

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_poverty)) +
  scale_fill_viridis_b() +
  theme_void()
```

# unemployed

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_unemployed)) +
  scale_fill_viridis_b() +
  theme_void()
```

# per capita income 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_capita_income)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent of population less than HS education 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_less_hs_grad)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent ESL 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_esl)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent under age 17 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_under_17)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent age 65 and older  

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_over_65)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent disabled 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_disabled)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent living in multi unit structure 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_multi_dwell)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent living in mobile dwelling 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_mobile_dwell)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent living in crowded dwelling 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_crowd_dwell)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent with no vehicle access 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_no_veh_avail)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent living in group quarters 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = per_group_dwell)) +
  scale_fill_viridis_b() +
  theme_void()
```

# percent minority 

```{r}
census_tract_data_spatial %>%
  ggplot() +
  geom_sf(mapping = aes(fill = minority)) +
  scale_fill_viridis_b() +
  theme_void()
```